### 2025-04-09 backmatter/appendices.tex
T-1 day to initial submission, nearly complete draft up to citations and small comments.

The Mellin transform was an important tool for us in capturing the behavior of the partonic cascade and associated correlations in \Secs{partonshower}{eec}.
%
In particular, the Mellin transform is used to study the scaling properties of functions.
%
In \Sec{jets}, we touched upon this briefly in a footnote.
%
We said:

@@

An important mathematical piece in our analysis of the splitting of trees and the sharing of momentum in the partonic cascade was the \textit{Mellin convolution}.
%
The Mellin convolution is defined by the following formal relation:
\begin{align}
    \label{eq:convolution-property}
    \mathcal{M}[f \mellinconvolution g](s)
    =
    \mathcal{M}[f](s) \, \mathcal{M}[g](s)
    \,.
\end{align}
In other words, a \vocab{Mellin convolution} of two functions \(f\) and \(g\) is a bi-linear map of the functions whose Mellin transform is the product of the individual Mellin transforms of \(f\) and \(g\).
%
Since it is a bi-linear map of the two functions, it seems natural to express it as an integral.
%
In particular,
\begin{proposition}{Mellin Convolution}{mellin-convolution-app}
    The \vocab{Mellin convolution}
    \begin{align}
        (f \mellinconvolution g)(x)
        =
        \int_0^\infty \frac{\dd y}{y}\, f(y) g(x/y)
        \,,
    \end{align}
    satisfies the natural convolution property of \Eq{convolution-property}.
\end{proposition}
%
We have seen this convolution in our exploration of the scaling behavior of parton showers in \Sec{partonshower} (and thus in the behavior of the resummed \gls{eec} in \Sec{eec}), and even in our exploration of parton-to-hadron fragmentation in \Prob{p2h-fragmentation}.
%
The proof of this result is left to \Prob{mellinconvolution}

>>>>

The Mellin transform was an important tool for us in capturing the behavior of the partonic cascade and associated correlations in \Secs{parton-shower}{eec}.
%
In particular, the Mellin transform is used to study the scaling properties of functions.
%
In \Sec{jets}, we touched upon this briefly in a footnote.
%
We said:

@@

An important mathematical piece in our analysis of the splitting of trees and the sharing of momentum in the partonic cascade was the \textit{Mellin convolution}.
%
The Mellin convolution is defined by the following formal relation:
\begin{align}
    \label{eq:convolution-property}
    \mathcal{M}[f \mellinconvolution g](s)
    =
    \mathcal{M}[f](s) \, \mathcal{M}[g](s)
    \,.
\end{align}
In other words, a \vocab{Mellin convolution} of two functions \(f\) and \(g\) is a bi-linear map of the functions whose Mellin transform is the product of the individual Mellin transforms of \(f\) and \(g\).
%
Since it is a bi-linear map of the two functions, it seems natural to express it as an integral.
%
In particular,
\begin{proposition}{Mellin Convolution}{mellin-convolution-app}
    The \vocab{Mellin convolution}
    \begin{align}
        (f \mellinconvolution g)(x)
        =
        \int_0^\infty \frac{\dd y}{y}\, f(y) g(x/y)
        \,,
    \end{align}
    satisfies the natural convolution property of \Eq{convolution-property}.
\end{proposition}
%
We have seen this convolution in our exploration of the scaling behavior of parton showers in \Sec{parton-shower} (and thus in the behavior of the resummed \gls{eec} in \Sec{eec}), and even in our exploration of parton-to-hadron fragmentation in \Prob{p2h-fragmentation}.
%
The proof of this result is left to \Prob{mellinconvolution}
